Composing like a human

### 2019-04-19 paper/main.tex
updated with many

@@

\usepackage{titlesec, blindtext, color}
\definecolor{gray75}{gray}{0.75}
\newcommand{\hsp}{\hspace{10pt}}
\titleformat{\chapter}[hang]{\Huge\bfseries}{\textcolor{gray75}{\thechapter \hsp \vline}\hsp}{0pt}{\Huge\bfseries}

@@

% Links
\usepackage{hyperref}

@@

\begin{titlepage}
    \begin{center}
        \huge\textbf{Thesis Title}
        \normalsize

@@

        \textbf{Tudor Paisa}\\
        SNR: 2019551 | ANR: 315146\\
        t.paisa@tilburguniversity.edu\\

@@

\chapter{Introduction}

The reemergence of neural networks (NN) has brought new ways to tackle Machine Learning problems (such as classification; see \cite{lecun_deep_2015} for several examples), as well as new possibilities to further artificial intelligence research (such as chatbots, or general-purpose AI systems; e.g., \cite{dale_return_2016} and \cite{vinyals_starcraft_2017} respectively). Currently, two exciting areas of research in the field of Deep Learning (DL) are in designing generative models \parencite{goodfellow_nips_2016} and training NNs on small datasets \parencite{finn_model-agnostic_2017, nichol_first-order_2018}. This research will combine both of these tasks by exploring the extent to which generative models can create novel and qualitative samples of music under the constraints posed by the few-shot learning problem. In other words, when data is scarce, can a generative model create samples of music that are new (i.e., not in the training set), consistent with common scales, and diverse (tone sequences are not repeated over and over, combines chord structures with single-note sequences, is not restricted to - say - one octave). This research will evaluate the generated samples of two state-of-the-art generative models (C-RNN-GAN of \cite{mogren_c-rnn-gan_2016} and Performance-RNN of \cite{oore_this_2018}) that have been trained under the Reptile learning framework \parencite{nichol_first-order_2018} on small amounts of MIDI data.

DL as a field, promises to discover rich hierarchical models \parencite{lecun_deep_2015}, over various artificial intelligence applications, such as speech recognition, image classification, or text generation. The majority of developments usually involved discriminative models \parencite{goodfellow_generative_2014}, where high-dimensional input is assigned to a class label \parencite{zhang_character-level_2015, krizhevsky_imagenet_2012}. In contrast, successes in generative models have been scarce, with Fully Visible Belief Networks \parencite{frey_does_1996} being the most suitable for the longest run, followed years later by Bidirectional Long Short Term Memory \parencite{graves_generating_2013} and Variational Autoencoders \parencite{kingma_auto-encoding_2013}.

However, studies on generative architectures were fairly uncommon until the discovery of the Generative Adversarial Network (GAN) by \textcite{goodfellow_generative_2014}. GANs have had significant successes in image super-resolution \parencite[; see Figure \ref{fig:srgan}]{ledig_photo-realistic_2016}, style-based image generation \parencite{karras_style-based_2018}, image-to-image translation such as a satellite image into a map, or a sketch into a photorealistic image \parencite[;see Figure \ref{fig:pix2pix}]{isola_image--image_2016}.

@@

@@

@@

\chapter{Methods}

>>>>

\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkColor[gray]{0.9}

@@

\usepackage{titlesec, blindtext, xcolor}
\definecolor{gray75}{gray}{0.75}
\definecolor{base00}{HTML}{fafafa}
\definecolor{base01}{HTML}{d4d4d4}
\definecolor{base02}{HTML}{abacae}
\definecolor{base03}{HTML}{7e8087}
\definecolor{base04}{HTML}{555761}
\definecolor{base05}{HTML}{333333}
\definecolor{base06}{HTML}{4d4d4d}
\definecolor{base07}{HTML}{666666}
\definecolor{base08}{HTML}{a10705}
\definecolor{base09}{HTML}{0d52bf}
\definecolor{base0A}{HTML}{cc3b02}
\definecolor{base0B}{HTML}{57392d}
\definecolor{base0C}{HTML}{d48e15}
\definecolor{base0D}{HTML}{3a9104}
\definecolor{base0E}{HTML}{7239b3}
\definecolor{base0F}{HTML}{667885}

\newcommand{\hsp}{\hspace{10pt}}
\titleformat{\chapter}[hang]{\Huge\bfseries}{\textcolor{base02}{\thechapter \hsp \vline}\hsp}{0pt}{\Huge\bfseries}
\titleformat{\section}[hang]{\Large\bfseries}{\textcolor{base01}{\thesection \hsp \vline}\hsp}{0pt}{\Large\bfseries}
\titleformat{\subsection}[hang]{\large\bfseries}{\textcolor{base01}{\thesubsection \hsp \vline}\hsp}{0pt}{\large\bfseries}

@@

% Links
\usepackage[colorlinks=true, citecolor=base08, linkcolor=base08, urlcolor=base08]{hyperref}

@@

\begin{titlepage}
    \begin{center}
        \huge\textbf{Composing like a human:} \\
        \Large\textbf{Adapting generative networks to few-shot learning in the musical domain}
        \normalsize

@@

        \textbf{Tudor Paisa}\\
        Student Number: 2019551 \\
        Administration Number: 315146\\
        t.paisa@tilburguniversity.edu\\

@@

\chapter{The return of the Neural Net}

Over the past sixty years, Artificial Neural Networks (ANNs) have experienced a number of cycles in popularity noted by extensive publicity of over-inflated expectations on the promises of connectionism (the field of science that tries to explain mental phenomena with the help of ANNs [CITATION NEEDED]): that a system could learn to do anything it was programmed to do [CITATION NEEDED] \parencite{minsky_perceptrons_1988}. However, each wave of praise was followed by a mass of public disappointment, criticism, and funding cuts [CITATION NEEDED]. These upturns and downturns of the field of connectionism - or more generally A.I. - are now known in the literature as the A.I. winters [CITATION NEEDED].

The recent revival of ANNs under the scope of Deep Learning (DL) has brought new ways to tackle Machine Learning problems, most notably in the context of classification (but also regression, although less popular; see \cite{lecun_deep_2015} for several examples of DL applications). In addition, with the advent of chatbots \parencite{dale_return_2016}, voice-activated personal assistants \parencite{xiong_microsoft_2018}, and general-purpose A.I. systems \parencite{vinyals_starcraft_2017}, DL introduced new frontiers in artificial intelligence research.

% NOTE: USE ME LATER
% Currently, two exciting areas of research in the field of Deep Learning (DL) are in designing generative models \parencite{goodfellow_nips_2016} and training NNs on small datasets \parencite{finn_model-agnostic_2017, nichol_first-order_2018}. This research will combine both of these tasks by exploring the extent to which generative models can create novel and qualitative samples of music under the constraints posed by the few-shot learning problem. In other words, when data is scarce, can a generative model create samples of music that are new (i.e., not in the training set), consistent with common scales, and diverse (tone sequences are not repeated over and over, combines chord structures with single-note sequences, is not restricted to - say - one octave). This research will evaluate the generated samples of two state-of-the-art generative models (C-RNN-GAN of \cite{mogren_c-rnn-gan_2016} and Performance-RNN of \cite{oore_this_2018}) that have been trained under the Reptile learning framework \parencite{nichol_first-order_2018} on small amounts of MIDI data.

Broadly speaking, DL as a field, promises to solve tasks which are easily (intuitively) performed by people, but hard to formalize \parencite[e.g., recognizing faces or spoken word;][]{goodfellow_deep_2016}. The solution comprises of enabling computers to learn form experience and understand the world through the discovery of hierarchical relationships between concepts \parencite{lecun_deep_2015}. This way, there is no need for manual input on the sort of knowledge that the computer needs \parencite{goodfellow_deep_2016}. A more simplistic and concise interpretation of DL would be to see it as a statistical technique for identifying patterns in sample data using large (deep) ANNs \parencite{marcus_deep_2018}.

The reasons for presenting these facts will be clarified in the following sections however, a terse argumentation is that progress towards general A.I. systems is marked by scant explorations of ANNs outside of the classification task, and even more so when trying to overcome some of their shortcomings, such as being highly reliant on massive amounts of data [CITATION NEEDED].
% NOTE: Maybe I was too harsh?

\section{We do not discriminate}\label{sec:no_disc}

Typically, in a neural network, the data samples go through a set of input units (that might represent pixels, word embeddings, etc.), then through multiple hidden layers, each with a given number of nodes, and reaching the output units where the answer is given \parencite{marcus_deep_2018}. An overwhelming majority of experiments with ANNs involve discriminative models \parencite{goodfellow_generative_2014}, where the goal is to assign the high-dimensional inputs to a class label \parencite[such as an animal or piece of furniture;][]{zhang_character-level_2015, krizhevsky_imagenet_2012}. However, other possible applications of DL models include (but are not limited to): regression [CITATION NEEDED], data compression \parencite{cheng_deep_2018}, and generating new data points \parencite{graves_generating_2013}.

For the purposes of this paper (see Section \ref{sec:thesis_goal}), generative model are central to our experiments (Chapter \ref{chap:methods}). Borrowing the analogy from \textcite{goodfellow_nips_2016}, one might wonder what is the value of studying generative models. After all, in the image domain, such a framework would merely generate more images (something which the Internet as no shortage of). Some of the more eloquent answers include using generative models for simulating possible futures to be later used for planning [CITATION NEEDED], providing predictions to missing data, or enabling work on multi-modal outputs, where a single input may have more than one correct answer \parencite{goodfellow_nips_2016}.

However, successes in generative models have been scarce, with Fully Visible Belief Networks \parencite{frey_does_1996} being the most suitable (and popular) method for the longest run. Yet, this method requires generating each sample one at a time (ramping up the cost of the process to $O(n)$). Coupled with the fact that the computation is done through a neural network, creating $n$ samples requires a substantial amount of time \parencite{goodfellow_nips_2016}. Variational Autoencoders \parencite{kingma_auto-encoding_2013} are another popular method that is used for this sort of task. Their main drawback is that when a weak approximation of a prior or posterior distribution of the data is used, the model might learn something other than the true data distribution \parencite{goodfellow_nips_2016}.

The discovery of Generative Adversarial Networks \parencite[GANs;][]{goodfellow_generative_2014} has leapfrogged the state of developments in this field. Besides countering the drawbacks outlined above \parencite{goodfellow_nips_2016}, they have been particularly successful at a variety of tasks such as image super-resolution \parencite[; see Figure \ref{fig:srgan}]{ledig_photo-realistic_2016}, style-based image generation \parencite{karras_style-based_2018}, or image-to-image translation \parencite[such as converting a satellite image into a map, or a sketch into a photorealistic image;][;see Figure \ref{fig:pix2pix}]{isola_image--image_2016}.

Although not as popular as the abovementioned, Recurrent Neural Networks (RNNs) have been successfully implemented for various generative tasks \parencite{jenal_rnn-based_2019, ICML2011Sutskever_524}. More specifically, a variation of these, Long Short-Term Memory Networks \parencite[LSTMs;][]{hochreiter_long_1997}, are of particular interest to this task. RNNs (and by extension LSTMs) contain a high-dimensional hidden state which allows them to remember and predict from previous inputs \parencite{ICML2011Sutskever_524}. This makes them great candidates for predicting sequences \parencite{graves_generating_2013} of text or characters, where the input at $t_0$ might be influenced by prior input at $t_{-1}$, $t_{-2}$, etc \parencite{fan_tts_2014}.

@@

\section{"Just... One more bite"}\label{sec:hungry}

@@

\section{Making music like a hooman} \label{sec:thesis_goal}

@@

\chapter{Methods}\label{chap:methods}

### 2019-04-19 paper/presentation.tex
updated with many

\title[Composing like a human]{Composing like a human}
\subtitle{Adapting generative networks to few-shot learning in the musical domain}
\author{Tudor Paisa  \texorpdfstring{\\ (SNR: 2019551, ANR: 315146)} \and \texttt{t.paisa@tilburguniversity.edu} }
\institute{Tilburg University}
\date{\today}

@@

\begin{frame}
    \frametitle{Outline}
    \tableofcontents
\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \section{Introduction}
    \subsection{Deep Learning}
    \begin{itemize}
        \item Deep Learning promises to discover rich hierarchical models over various applications
    \end{itemize}

\end{frame}

>>>>

\title[Composing like a human]{Composing like a human}
\subtitle{Adapting generative networks to few-shot learning in the musical domain}
\author{Tudor Paisa  \texorpdfstring{\\ (SNR: 2019551, ANR: 315146)}{} \texorpdfstring{\\ \texttt{t.paisa@tilburguniversity.edu}}{} }
\institute{Tilburg University}
\date{\today}

@@

%\begin{frame}
    %\frametitle{Outline}
    %\tableofcontents
%\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \section{Introduction}
    \begin{block}{Deep Learning}
    \begin{itemize}
        \item Deep Learning promises to discover rich hierarchical models over various applications
        \item The majority of developments usually involve discriminative models
        \item In recent years...
            \begin{itemize}
            \item Generative Models
            \item Few-Shot Learning
            \end{itemize}
    \end{itemize}
\end{block}
\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \begin{block}{Generative Models}
        \begin{itemize}
            \item A Neural Network that is able to generate data
            \item Simple concept...
                \begin{itemize}
                    \item ... slow developments...
                \end{itemize}
            \item ... until frameworks like GANs \& LSTM
            \item Widely researched in Computer Vision, Natural Language Processing, not so much in arts (music especially)
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \begin{block}{Few-Shot Learning}
        \begin{itemize}
            \item Neural Networks tend to be "data-hungry"
            \item SGD does not allow convergence in a limited number of steps
            \item For AI applications this sucks
                \begin{itemize}
                    \item Humans generalize after one/few examples
                    \item Vanilla neural nets do not
                \end{itemize}
            \item Few-Shot Learning: making neural networks generalize using by showing it few instances of each class
            \item Solutions? Yes! More on that later
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \begin{block}{Getting There...}
        \begin{itemize}
            \item Overwhelming majority of few-shot generative developments have been in Computer Vision
            \item Then some in Natural Language Processing
            \item Musical domain largely unexplored
        \end{itemize}
    \end{block}

    \begin{block}{The research!}
        \begin{itemize}
            \item Adapt two generative models to few-shot learning
            \item Evaluate their ability to create music
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}
    \frametitle{Theoretical Framework}
    \begin{block}{Music Generators}
        There are two candidates:
    \end{block}
        \begin{block}{C-RNN-GAN}
            \begin{minipage}[b]{0.48\textwidth}
                $G$enerator \\
                2 $\times$ \textbf{unidirectional} LSTM \\
                350 hidden units
            \end{minipage}
            \hfill
            \begin{minipage}[b]{0.48\textwidth}
                $D$iscriminator \\
                2 $\times$ \textbf{bidirectional} LSTM \\
                350 hidden units
            \end{minipage}
        \end{block}
        \begin{block}{PerformanceRNN}
            3 $\times$ \textbf{unidirectional} LSTM \\
            512 hidden units
        \end{block}
\end{frame}

### 2019-04-19 paper/thesis.tex
updated with many

\documentclass[a4paper]{book}

\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkColor[gray]{0.9}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{titlesec, blindtext, xcolor}
\definecolor{gray75}{gray}{0.75}
\definecolor{base00}{HTML}{fafafa}
\definecolor{base01}{HTML}{d4d4d4}
\definecolor{base02}{HTML}{abacae}
\definecolor{base03}{HTML}{7e8087}
\definecolor{base04}{HTML}{555761}
\definecolor{base05}{HTML}{333333}
\definecolor{base06}{HTML}{4d4d4d}
\definecolor{base07}{HTML}{666666}
\definecolor{base08}{HTML}{a10705}
\definecolor{base09}{HTML}{0d52bf}
\definecolor{base0A}{HTML}{cc3b02}
\definecolor{base0B}{HTML}{57392d}
\definecolor{base0C}{HTML}{d48e15}
\definecolor{base0D}{HTML}{3a9104}
\definecolor{base0E}{HTML}{7239b3}
\definecolor{base0F}{HTML}{667885}

\newcommand{\hsp}{\hspace{10pt}}
\titleformat{\chapter}[hang]{\Huge\bfseries}{\textcolor{base02}{\thechapter \hsp \vline}\hsp}{0pt}{\Huge\bfseries}
\titleformat{\section}[hang]{\Large\bfseries}{\textcolor{base01}{\thesection \hsp \vline}\hsp}{0pt}{\Large\bfseries}
\titleformat{\subsection}[hang]{\large\bfseries}{\textcolor{base01}{\thesubsection \hsp \vline}\hsp}{0pt}{\large\bfseries}

\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{references.bib}

% Essentials
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[ruled]{algorithm2e}

% Typography
\usepackage{palatino}
\usepackage{fontenc}

% Links
\usepackage[colorlinks=true, citecolor=base08, linkcolor=base08, urlcolor=base08]{hyperref}

% Math stuff
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{bm}

% Commands
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\begin{document}

\begin{titlepage}
    \begin{center}
        \huge\textbf{Composing like a human:} \\
        \Large\textbf{Adapting generative networks to few-shot learning in the musical domain}
        \normalsize

        \vspace{1cm}

        \textbf{Tudor Paisa}\\
        Student Number: 2019551 \\
        Administration Number: 315146\\
        t.paisa@tilburguniversity.edu\\

        \vspace{1cm}
        \textsc{Thesis submitted in partial fulfillment\\
        of the requirements for the degree of\\
        Master of Science in Data Science and Society,\\
        at the School of Humanities and Digital Sciences\\
        of Tilburg University\\}

        \vspace{2cm}
        Thesis Committee:\\
        Dr. Menno van Zaanen\\
        Dr. SECOND READER\\
        \vfill

        Tilburg University\\
        School of Humanities and Digital Sciences\\
        Department of Cognitive Science \& Artificial Intelligence\\
        Tilburg, The Netherlands\\
        \today

    \end{center}
\end{titlepage}

\chapter*{Abstract}
    Lorem Ipsum

\tableofcontents

\chapter{The return of the Neural Net}

Over the past sixty years, Artificial Neural Networks (ANNs) have experienced a number of cycles in popularity noted by extensive publicity of over-inflated expectations on the promises of connectionism (the field of science that tries to explain mental phenomena with the help of ANNs [CITATION NEEDED]): that a system could learn to do anything it was programmed to do [CITATION NEEDED] \parencite{minsky_perceptrons_1988}. However, each wave of praise was followed by a mass of public disappointment, criticism, and funding cuts [CITATION NEEDED]. These upturns and downturns of the field of connectionism - or more generally A.I. - are now known in the literature as the A.I. winters [CITATION NEEDED].

The recent revival of ANNs under the scope of Deep Learning (DL) has brought new ways to tackle Machine Learning problems, most notably in the context of classification (but also regression, although less popular; see \cite{lecun_deep_2015} for several examples of DL applications). In addition, with the advent of chatbots \parencite{dale_return_2016}, voice-activated personal assistants \parencite{xiong_microsoft_2018}, and general-purpose A.I. systems \parencite{vinyals_starcraft_2017}, DL introduced new frontiers in artificial intelligence research.

% NOTE: USE ME LATER
% Currently, two exciting areas of research in the field of Deep Learning (DL) are in designing generative models \parencite{goodfellow_nips_2016} and training NNs on small datasets \parencite{finn_model-agnostic_2017, nichol_first-order_2018}. This research will combine both of these tasks by exploring the extent to which generative models can create novel and qualitative samples of music under the constraints posed by the few-shot learning problem. In other words, when data is scarce, can a generative model create samples of music that are new (i.e., not in the training set), consistent with common scales, and diverse (tone sequences are not repeated over and over, combines chord structures with single-note sequences, is not restricted to - say - one octave). This research will evaluate the generated samples of two state-of-the-art generative models (C-RNN-GAN of \cite{mogren_c-rnn-gan_2016} and Performance-RNN of \cite{oore_this_2018}) that have been trained under the Reptile learning framework \parencite{nichol_first-order_2018} on small amounts of MIDI data.

Broadly speaking, DL as a field, promises to solve tasks which are easily (intuitively) performed by people, but hard to formalize \parencite[e.g., recognizing faces or spoken word;][]{goodfellow_deep_2016}. The solution comprises of enabling computers to learn form experience and understand the world through the discovery of hierarchical relationships between concepts \parencite{lecun_deep_2015}. This way, there is no need for manual input on the sort of knowledge that the computer needs \parencite{goodfellow_deep_2016}. A more simplistic and concise interpretation of DL would be to see it as a statistical technique for identifying patterns in sample data using large (deep) ANNs \parencite{marcus_deep_2018}.

The reasons for presenting these facts will be clarified in the following sections however, a terse argumentation is that progress towards general A.I. systems is marked by scant explorations of ANNs outside of the classification task, and even more so when trying to overcome some of their shortcomings, such as being highly reliant on massive amounts of data [CITATION NEEDED].
% NOTE: Maybe I was too harsh?

\section{We do not discriminate}\label{sec:no_disc}

Typically, in a neural network, the data samples go through a set of input units (that might represent pixels, word embeddings, etc.), then through multiple hidden layers, each with a given number of nodes, and reaching the output units where the answer is given \parencite{marcus_deep_2018}. An overwhelming majority of experiments with ANNs involve discriminative models \parencite{goodfellow_generative_2014}, where the goal is to assign the high-dimensional inputs to a class label \parencite[such as an animal or piece of furniture;][]{zhang_character-level_2015, krizhevsky_imagenet_2012}. However, other possible applications of DL models include (but are not limited to): regression [CITATION NEEDED], data compression \parencite{cheng_deep_2018}, and generating new data points \parencite{graves_generating_2013}.

For the purposes of this paper (see Section \ref{sec:thesis_goal}), generative model are central to our experiments (Chapter \ref{chap:methods}). Borrowing the analogy from \textcite{goodfellow_nips_2016}, one might wonder what is the value of studying generative models. After all, in the image domain, such a framework would merely generate more images (something which the Internet as no shortage of). Some of the more eloquent answers include using generative models for simulating possible futures to be later used for planning [CITATION NEEDED], providing predictions to missing data, or enabling work on multi-modal outputs, where a single input may have more than one correct answer \parencite{goodfellow_nips_2016}.

However, successes in generative models have been scarce, with Fully Visible Belief Networks \parencite{frey_does_1996} being the most suitable (and popular) method for the longest run. Yet, this method requires generating each sample one at a time (ramping up the cost of the process to $O(n)$). Coupled with the fact that the computation is done through a neural network, creating $n$ samples requires a substantial amount of time \parencite{goodfellow_nips_2016}. Variational Autoencoders \parencite{kingma_auto-encoding_2013} are another popular method that is used for this sort of task. Their main drawback is that when a weak approximation of a prior or posterior distribution of the data is used, the model might learn something other than the true data distribution \parencite{goodfellow_nips_2016}.

The discovery of Generative Adversarial Networks \parencite[GANs;][]{goodfellow_generative_2014} has leapfrogged the state of developments in this field. Besides countering the drawbacks outlined above \parencite{goodfellow_nips_2016}, they have been particularly successful at a variety of tasks such as image super-resolution \parencite[; see Figure \ref{fig:srgan}]{ledig_photo-realistic_2016}, style-based image generation \parencite{karras_style-based_2018}, or image-to-image translation \parencite[such as converting a satellite image into a map, or a sketch into a photorealistic image;][;see Figure \ref{fig:pix2pix}]{isola_image--image_2016}.

Although not as popular as the abovementioned, Recurrent Neural Networks (RNNs) have been successfully implemented for various generative tasks \parencite{jenal_rnn-based_2019, ICML2011Sutskever_524}. More specifically, a variation of these, Long Short-Term Memory Networks \parencite[LSTMs;][]{hochreiter_long_1997}, are of particular interest to this task. RNNs (and by extension LSTMs) contain a high-dimensional hidden state which allows them to remember and predict from previous inputs \parencite{ICML2011Sutskever_524}. This makes them great candidates for predicting sequences \parencite{graves_generating_2013} of text or characters, where the input at $t_0$ might be influenced by prior input at $t_{-1}$, $t_{-2}$, etc \parencite{fan_tts_2014}.

@@

\section{"Just... One more bite"}\label{sec:hungry}

@@

\section{Making music like a hooman} \label{sec:thesis_goal}

@@

\chapter{Methods}\label{chap:methods}

@@

\end{document}

>>>>

%\documentclass[a4paper]{book}

%\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}

%\usepackage{titlesec, blindtext, color}
%\definecolor{gray75}{gray}{0.75}
%\newcommand{\hsp}{\hspace{10pt}}
%\titleformat{\chapter}[hang]{\Huge\bfseries}{\textcolor{gray75}{\thechapter \hsp \vline}\hsp}{0pt}{\Huge\bfseries}

%\usepackage[american]{babel}
%\usepackage{csquotes}
%\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
%\DeclareLanguageMapping{american}{american-apa}
%\addbibresource{references.bib}

%% Essentials
%\usepackage{tabularx}
%\usepackage{graphicx}
%\usepackage{subcaption}
%\usepackage[ruled]{algorithm2e}

%% Typography
%\usepackage{palatino}
%\usepackage{fontenc}

%% Links
%\usepackage{hyperref}

%% Math stuff
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{amstext}
%\usepackage{bm}

%% Commands
%\DeclareMathOperator*{\argmin}{arg\,min}
%\DeclareMathOperator*{\argmax}{arg\,max}

%\begin{document}

%\begin{titlepage}
%    \begin{center}
%        \huge\textbf{Thesis Title}
%        \normalsize

%        \vspace{1cm}

%        \textbf{Tudor Paisa}\\
%        SNR: 2019551 | ANR: 315146\\
%        t.paisa@tilburguniversity.edu\\

%        \vspace{1cm}
%        \textsc{Thesis submitted in partial fulfillment\\
%        of the requirements for the degree of\\
%        Master of Science in Data Science and Society,\\
%        at the School of Humanities and Digital Sciences\\
%        of Tilburg University\\}

%        \vspace{2cm}
%        Thesis Committee:\\
%        Dr. Menno van Zaanen\\
%        Dr. SECOND READER\\
%        \vfill

%        Tilburg University\\
%        School of Humanities and Digital Sciences\\
%        Department of Cognitive Science \& Artificial Intelligence\\
%        Tilburg, The Netherlands\\
%        \today

%    \end{center}
%\end{titlepage}

%\chapter*{Abstract}
%    Lorem Ipsum

%\tableofcontents

\chapter{Introduction}

The reemergence of neural networks (NN) has brought new ways to tackle Machine Learning problems (such as classification; see \cite{lecun_deep_2015} for several examples), as well as new possibilities to further artificial intelligence research (such as chatbots, or general-purpose AI systems; e.g., \cite{dale_return_2016} and \cite{vinyals_starcraft_2017} respectively). Currently, two exciting areas of research in the field of Deep Learning (DL) are in designing generative models \parencite{goodfellow_nips_2016} and training NNs on small datasets \parencite{finn_model-agnostic_2017, nichol_first-order_2018}. This research will combine both of these tasks by exploring the extent to which generative models can create novel and qualitative samples of music under the constraints posed by the few-shot learning problem. In other words, when data is scarce, can a generative model create samples of music that are new (i.e., not in the training set), consistent with common scales, and diverse (tone sequences are not repeated over and over, combines chord structures with single-note sequences, is not restricted to - say - one octave). This research will evaluate the generated samples of two state-of-the-art generative models (C-RNN-GAN of \cite{mogren_c-rnn-gan_2016} and Performance-RNN of \cite{oore_this_2018}) that have been trained under the Reptile learning framework \parencite{nichol_first-order_2018} on small amounts of MIDI data.

DL as a field, promises to discover rich hierarchical models \parencite{lecun_deep_2015}, over various artificial intelligence applications, such as speech recognition, image classification, or text generation. The majority of developments usually involved discriminative models \parencite{goodfellow_generative_2014}, where high-dimensional input is assigned to a class label \parencite{zhang_character-level_2015, krizhevsky_imagenet_2012}. In contrast, successes in generative models have been scarce, with Fully Visible Belief Networks \parencite{frey_does_1996} being the most suitable for the longest run, followed years later by Bidirectional Long Short Term Memory \parencite{graves_generating_2013} and Variational Autoencoders \parencite{kingma_auto-encoding_2013}.

However, studies on generative architectures were fairly uncommon until the discovery of the Generative Adversarial Network (GAN) by \textcite{goodfellow_generative_2014}. GANs have had significant successes in image super-resolution \parencite[; see Figure \ref{fig:srgan}]{ledig_photo-realistic_2016}, style-based image generation \parencite{karras_style-based_2018}, image-to-image translation such as a satellite image into a map, or a sketch into a photorealistic image \parencite[;see Figure \ref{fig:pix2pix}]{isola_image--image_2016}.

@@

@@

@@

\chapter{Methods}

@@

%\end{document}
